Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-10-25 Ch1_movement_rates/Ch1_Figures.Rmd
I think I did something stupid and now the third panel isn't showing colors.

movrate_cp
movrate_np
movrate_pp

@@

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002, color = fam_g)) +
  geom_point(size = 3, alpha = 0.8) +
  # geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Lognormal fit to individual movement rates") +
  #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70)) +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = "none") -> logfit_plot

@@

movratedf %>% 
  ggplot(., aes(x = movrate, y = factor(scenario, levels = c("pp", "np", "cp")), color = as.character(group))) +
  geom_point(size = 3, alpha = 0.8) +
  scale_color_manual(values = cols.fig2) +
  scale_x_continuous(limits = c(0, 70)) +
  labs(x = "Movement Rate (meters/minute)", y = "Model scenario",
       title = "Sampled movement rates for each simulated scenario") +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = "none") -> movrates_used

>>>>

# movrate_cp
# movrate_np
# movrate_pp

@@

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002, color = fam_g)) +
  geom_point(size = 3, alpha = 0.8) +
  # geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Lognormal fit to individual movement rates") +
  #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70)) +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  #theme(legend.position = "none") +
  NULL -> logfit_plot

@@

movratedf %>% 
  ggplot(., aes(x = movrate, y = factor(scenario, levels = c("pp", "np", "cp")), color = as.character(group))) +
  geom_point(size = 3, alpha = 0.8) +
  scale_color_manual(values = cols.fig2) +
  scale_x_continuous(limits = c(0, 70)) +
  labs(x = "Movement Rate (meters/minute)", y = "Model scenario",
       title = "Sampled movement rates for each simulated scenario") +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  #theme(legend.position = "none") +
  NULL-> movrates_used
